Cluster Detection from three-dimensional Lensing Mass Map

### 2021-01-08 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex
add detection density to paper
add discussion on the detection number density

>>>>

According to the detection rate measured from the simulation, we predict the
number density of detected cluster using the halo mass function of
\citet{haloMass-Tinker2008}. We use HMF \citep{hmf-Murray2013}, an open-source
package, to calculate the halo mass function.  The predicted halo detection
number density for the setup ($\lambda=5$, $1.5\sigma$ detection threshold) is
shown in Figure \ref{fig_detNum}. The expected cluster number density in total
is $0.49$ $\deg^{-2}$, which is $78.4$ clusters for the first year HSC shear
catalog \citep{HSC1-catalog} with a survey area of $\sim 160 \deg^2$.

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{detNum_zm.pdf}
 \caption{The expected number density of detected clusters per square degree as
     a function of halo's virial mass and redshift. The number density in total
     is $0.49~\deg^{-2}$.
     } \label{fig_detNum}
\end{figure}
